---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# robinlovelace

This is the source code of my website.
I plan to store notes on how to use it here.

New talk:


```{bash, eval=FALSE}
hugo new  --kind event event/ogh23
cp -Rv content/event/glasgow2024 content/event/st-andrews2025
code content/event/st-andrews2025/index.md
```

```{r}
# Equivalent copying code in R:
system("cp -Rv content/event/glasgow2024 content/event/st-andrews-2025")
file.copy("content/event/st-andrews-2025/index.qmd", "content/event/st-andrews-2025/index.Rmd", overwrite = TRUE)
```

```{r, eval=FALSE}
remotes::install_cran("blogdown")
file.edit("content/event/modeshift-2022/index.md")
blogdown::install_hugo()

# new blog post:
blogdown::new_post(title = "2024-retrospective", ext = ".Rmd")

blogdown::new_content(path = "software/index.Rmd")

# serve site
blogdown::serve_site()
blogdown::stop_server()

# build site
blogdown::build_site()
```

To update publications:

```bash
pip install --upgrade academic

# 1. Update the BibTeX file with new entries (from Zotero or manually)
academic import --overwrite --normalize static/bibs/my-citations-for-web.bib content/publication/
```

**⚠️ Known issues with `academic import --overwrite`:**

- **Abstracts are cleared** — the import sets `abstract: ''` for all pages. Restore from Zotero:
  ```bash
  # Extract abstracts from Zotero export and update index.md files
  python3 scripts/restore-abstracts.py
  ```
- **`publication_types` must be integers** — import may output strings like `"article-journal"`. Wowchemy requires: `0` = uncategorized, `2` = journal article, `5` = book. Fix:
  ```bash
  find content/publication/ -name "index.md" -exec sed -i 's/- article-journal$/- "2"/' {} \;
  ```
- **Featured publications reset** — `--overwrite` sets `featured: false` on all pages. Re-enable:
  ```bash
  # Set featured: true in index.md for key publications
  ```
- **Template placeholders** — import leaves `Add the **full text**...` placeholder text. Remove:
  ```bash
  find content/publication/ -name "index.md" -exec sed -i '/Add the \*\*full text\*\*/d' {} \;
  ```

**Adding new papers from Zotero:**

```bash
# Export from Zotero, compare DOIs, add missing entries to my-citations-for-web.bib
# Then run import and fix issues above
```


