---
title: Reflections on 2020 and ideas for 2021
author: ~
date: '2020-12-30'
slug: new-year-new-site-new-world
draft: false
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-01-01T16:01:42Z'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


2020 has been a crazy year all-round with US elections, Brexit negotiations reaching their conclusions and of course the global pandemic that has swept across countries and disrupted lives worldwide.

Looking back over the year a huge amount has changed and I wanted to take the opportunity of the new year to share some thoughts and update, providing an opportunity to post on my updated website ✨.

## Online teaching

I was lucky enough to work from home meaning that I could plough on with my research and teaching in ITS.
In fact, my first fully online-only taught lecture, part of the Transport Data Science module, was delivered on the 17^th^ March, as communicated in the Tweet below. 

```{r}
blogdown::shortcode("tweet", "1239930988416897033")
```

That was on 17th March, just one day after the Prime Minister advised against "non-essential" travel and in-person social interaction on [March 16th](https://en.wikipedia.org/wiki/Timeline_of_the_COVID-19_pandemic_in_the_United_Kingdom_(January%E2%80%93June_2020)#March_2020).
It was not until three days later that cafes, pubs and restaurants were closed.
