---
title: 'Cycleways in South and East Leeds: a Photoblog'
author: Robin Lovelace
date: '2021-04-11'
slug: cycleways-se-leeds
categories:
  - cycling
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-04-11T21:07:36+01:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tmap)
tmap_mode("view")
if(!file.exists("2021_04_11_11_31_Sun.gpx")) {
  download.file("https://www.openstreetmap.org/trace/3633523/data", "2021_04_11_11_31_Sun.gpx")
}
# sf::st_layers("2021_04_11_11_31_Sun.gpx")
route = sf::read_sf("2021_04_11_11_31_Sun.gpx", layer = "tracks")
ctown = tmaptools::geocode_OSM(q = "chapeltown leeds", as.sf = TRUE)
ctown_buffer = stplanr::geo_buffer(ctown, dist = 500)
route = sf::st_difference(route, ctown_buffer)
```


Taking advantage of a sunny Sunday, a friend and I decided to check-out the latest active travel infrastructure developments in South and East Leeds.
We planned the route around two destinations and one well-established route: 

- The [Leeds Climate Innovation District](https://citu.co.uk/citu-places), a new sustainability-focussed housing development being built near central Leeds
- [Temple Newsam](https://en.wikipedia.org/wiki/Temple_Newsam), a publicly accessible stately home and leisure grounds part-designed by prolific landscaper [Capability Brown](https://en.wikipedia.org/wiki/Capability_Brown) in the 1760s and now owned by [Leeds City Council](https://www.leeds.gov.uk/)
- The well-known [Wyke Beck Way](https://www.leeds.gov.uk/docs/Wyke%20Beck%20Way%20Cycle%20Route.pdf), which runs North from Temple Newsam to Roundhay Park

An overview of the route is shown below:

```{r, eval=FALSE}
s = c(
    # `Grey basemap` = "CartoDB.Positron",
    # `Coloured basemap` = "Esri.WorldTopoMap",
    `OSM existing cycle provision (CyclOSM)` = "https://tile.thunderforest.com/cycle/{z}/{x}/{y}.png?apikey=feae177da543411c9efa64160305212d",
    # `PCT commuting, Government Target` = "https://npttile.vs.mythic-beasts.com/commute/v2/govtarget/{z}/{x}/{y}.png",
    # `PCT schools, Government Target` = "https://npttile.vs.mythic-beasts.com/school/v2/govtarget/{z}/{x}/{y}.png",
    `Satellite image` = "https://server.arcgisonline.com/ArcGIS/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}'"
)
m = tm_shape(route) + tm_lines(lwd = 3) + tm_basemap(server = s) +
  tm_scale_bar() +
  tm_minimap(server = "Esri.WorldTopoMap")
tmap_save(m, "map-leeds-routes.html")
```

```{r}
knitr::include_url("map-leeds-routes.html")
```


## Leeds Climate Innovation District

Leeds Climate Innovation District (LCID) is a major development in Leeds, with 500+ dwellings either in the process of being built or already being lived in (at the time of writing in April 2021).
I cannot comment on the energy efficiency ratings of the buildings (although I have little doubt that they are well insulated) but in terms of its appearance and accessibility by walking and cycling it is ground-breaking.

I had heard of LCID and passed by it during early stages of construction but only appreciated its scale and level and ambition today after seeing the site.
In the spring sunshine it was stunning:


